Test data

### 2022-07-27 Dashboard/NGO Analysis dashboard alpha.Rmd

  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end
    )

    id <- showNotification(
      "Generating report...",
      duration = NULL,
      closeButton = FALSE
    )
    on.exit(removeNotification(id), add = TRUE)

    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
```

@@

  # All boxes use the colour "primary" and the icon fa-solid fa-circle-xmark" if
  # the value is NA

>>>>

  # Based on code in Mastering Shiny
  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

    # parameters
    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end
    )

    # notification
    id <- showNotification(
      "Generating report...",
      duration = NULL,
      closeButton = FALSE
    )
    on.exit(removeNotification(id), add = TRUE)

    # R Markdown render
    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
```

@@

  # All boxes use the colour "primary" and the icon "fa-solid fa-circle-xmark" if
  # the value is NA

### 2022-07-27 Old/Shiny/Test/Flexdashboard rows tests.Rmd

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools, purrr
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

Then upload an Excel file in the set format (available [here](https://github.com/amaliehc/ISSSV1337/blob/5c0a8a2beae499b3d2524a3965ceebf3b3ebad0e/Dashboard/Data/NGO_template.xltx)).

@@

If desired, a copy of the analysis in PDF format may then be downloaded.

```{r sidebar_button}
# download
uiOutput("downloadUI")
```

@@

Row {data-height=60}
-----------------------------------------------------------------------

### NGO analysed

```{r}
# Using htmlOutput() to use html styling
htmlOutput("title")
```

@@

- **Fundraising ROI**:
  - A basic measure of the return on investment of direct fundraising expenses:

  $$\frac{\text{private contributions} + \text{membership fees} - \text{fundraising expenses}}{\text{fundraising expenses}} \times 100$$

- **Liquid assets/obligations**:
  - A measure of the relationship between the organisation's liquid assets and its obligations:

  $$\frac{\text{private contributions} + \text{investment income} + \text{cash in bank and cash equivalents}}{\text{short term grants payable} + \text{revocable endowments} + \text{long term grants payable}} \times 100$$

- **Private donations growth**:
  - A calculation of the percentage change in private contributions based on the two most recent years:

  $$\frac{\text{private contributions}_2 - \text{private contributions}_1}{\text{private contributions}_1}\times 100$$

- **Public grants growth**:
  - A calculation of the percentage change in public grants received based on the two most recent years:

$$\frac{\text{public grants}_2 - \text{public grants}_1}{\text{public grants}_1} \times 100$$

- **Private/public proportion**:
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants:

$$\frac{\text{private contributions} + \text{membership fees}}{\text{public grants} + \text{private contributions} + \text{membership fees}} \times 100$$

@@

```{r value_boxes, include=FALSE}
# Shiny actions

# Report Output ==============================================================

output$downloadUI <- renderUI({
  downloadButton("report", "Download report")
})

output$report <- downloadHandler(

  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end
    )

    id <- showNotification(
      "Generating report...",
      duration = NULL,
      closeButton = FALSE
    )
    on.exit(removeNotification(id), add = TRUE)

    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)

observe({ # wait for button click

@@

  # NGO title ==================================================================
  NGO <- reactive({
    read_excel(input$excel$datapath) |>
      # Turning the needed column into a list
      pull(Firm) |>
      # discarding all NAs in case the name is somewhere
      purrr::discard(is.na) |>
      # choosing the first available name
      first()
  })

  title <- reactive({
    # testing if NGO() is NA
    if (is.na(NGO())) {
      # Printing warning if NA
      "Name of NGO missing"
      # Printing name of NGO
    } else {
      NGO()
    }
  })

  # Creating NGO title using html formatting (colour based on MetBrewer
  # "Hokusai2")
  output$title <- renderText({
    paste('<b><font size="5em" color="#2f70a1">', title(), "</font></b>")
  })

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

Then upload an Excel file in the set format.

@@

@@

@@

- **Fundraising ROI**: $$\frac{\text{private contributions} + \text{membership fees} - \text{fundraising expenses}}{\text{fundraising expenses}} \times 100$$
  - A basic measure of the ROI of direct fundraising expenses.
- **Liquid assets/obligations**: $$\frac{\text{private contributions} + \text{investment income} + \text{cash in bank and cash equivalents}}{\text{short term grants payable} + \text{revocable endowments} + \text{long term grants payable}} \times 100$$
  - A measure of the relationship between the organisation's liquid assets and its obligations.
- **Private donations growth**: $$\frac{\text{private contributions}_2 - \text{private contributions}_1}{\text{private contributions}_1}\times 100$$
  - A calculation of the percentage change in private contributions based on the two most recent years.
- **Public grants growth**: $$\frac{\text{public grants}_2 - \text{public grants}_1}{\text{public grants}_1} \times 100$$
  - A calculation of the percentage change in public grants received based on the two most recent years.
- **Private/public proportion**: $$\frac{\text{private contributions} + \text{membership fees}}{\text{public grants} + \text{private contributions} + \text{membership fees}} \times 100$$
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants.

@@

```{r value_boxes, include=FALSE}
# Shiny actions
observe({ # wait for button click

@@

### 2022-07-27 Old/Shiny/Test/Test data.Rmd

title <- if (length(NGO) == 0) {
  "Name of NGO missing"
} else {
  NGO
}

title
```

>>>>

title <- if (is.na(NGO)) {
  "Name of NGO missing"
} else {
  NGO
}

title

NGO_blank <- read_excel("Data/Bad_data_no_name.xlsx") |> 
  pull(Firm) |>
  first()

NGO_blank <- read_excel("Data/Bad_data_no_name.xlsx") |> 
  pull(Firm) |> 
  purrr::discard(is.na) |> 
  first()

length(NGO_blank)
